A Compound Decision Approach to Covariance Matrix Estimation

### 2021-10-02 response_reviews.tex

It has been removed.
\end{enumerate}
\section{Comments to Referee2}
\begin{enumerate}
\item \emph{In the numerical experiments and the real data analysis, what was the size of the grid that was used? I may have missed it but I did not see it mentioned in the caption for figure 2.}\\
In section 3.3, methods compared and section 3.4, data analysis, we used clustering-based exemplar algorithm, where we find $K$ clusters of all off-diagonal sample points. $K$ is set to be $p$ to balance accuracy and speed according to result of section 3.2.
\item \emph{In the numerical experiments, the dimension p goes as far as 200. I believe it will be useful to consider a setting where $n = 100$ and $p = 1000$.} \\
We did the simulation for $n=100$ and $p=1000$ using the different covariance matrix models in Section 3.1. Please see the supporting information for the simulation results.  
\item \emph{Continuing on the numerical experiments, models 1 to 5 impose various structures on $\bs{\Sigma}$. It will be interesting to see the performance of the proposed method if a spiked covariance structure is imposed on $\bs{\Sigma}$.} \\
We added the spiked model as the sixth matrix models in Section 3.1. Spiked covariance matrix is generated by $\Sigma = \bs{U}\text{diag}(\bs{l})\bs{U}^\top$, where $\bs{U}$ is a randomly generated orthogonal unit matrix, $\bs{l} = \{4,3,2,1,\ldots,1\}$.
\item \emph{Typo on page 6: "The density of $f(\cdot \mid \bs{\eta}_{jk})$ of ...".}\\
Thanks for poiting this out. We've fixed this sentence as "$f(\cdot \mid \bs{\eta}_{jk})$, the density of $\bs{A}_{jk}$, depends on $\bs{\eta}_{jk} = (\sigma_j, \sigma_k, r_{jk})^\top$, ...".
\end{enumerate}
\begin{thebibliography}{9}
\bibitem{dey2018}
Dey, K. K., \& Stephens, M. (2018). CorShrink: Empirical Bayes shrinkage estimation of correlations, with applications. bioRxiv, 368316.
\bibitem{ledoit2004}
Ledoit, O., \& Wolf, M. (2004). A well-conditioned estimator for large-dimensional covariance matrices. Journal of multivariate analysis, 88(2), 365-411.

\end{thebibliography}
\end{document}

### 2021-11-02 response_reviews.tex

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
%\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{multirow}
\usepackage{comment}
\usepackage{lscape}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\def\bs{\boldsymbol}
\def\bb{\mathbb}

\title{Response to reviews of BIOM2021236M}
\author{}
\date{}

\begin{document}
\maketitle

\section{Response to the Associate Editor}

\begin{enumerate}
\item \emph{As a journal, Biometrics presents papers that focus on the development of new methods and results of use in biosciences. As of now, the application seems more an afterthought, the use of a convenient (easily available) dataset to fit the scope of the journal. I believe that the authors should motivate their approach from the gene expression data or other bio-related applications starting from the Introduction.}
\item \emph{It is not really intuitively clear why the vectorization works, despite the approach not taking into consideration the structure of the covariance matrix. Also, the manuscript proposes a series of ad-hoc expedients to implement the method. See the clustering-based exemplar algorithm and replacing non-positive eigenvalues with a chosen positive value $c$ in the positive-definite correction. These expedients do not seem to be completely justified by the proposed separable compound-decision theory framework, and their effects on the estimation are unclear. A referee also commented on the impossibility to follow closely the implementation of the EM algorithm. In short, while I appreciate that the theoretical justification for the asymptotic efficiency of the proposed vectorization is not clear, the current implementation reads more like a clever algorithm than a well-founded statistical method. The authors should justify all the steps of the algorithm and provide an assessment of their contribution to its overall performance.}

@@

It has been fixed.

\emph{- In Equations (1) and (2) the arguments of the risk functions are $\theta$ and $\delta$. However, on page 5 the arguments of $\hat{R}$ are $\beta_{S}$, and $\beta_{I}$.}

We have changed the notation $\hat{R}$ to $\text{RE}$ which means risk estimator and this differentiates it from $R$. 
\end{enumerate}

\section{Comments to Referee1}
Thank you so much for the detailed and inspiring suggestions on our paper. We learnt a lot through them. We agree with your comments and address them in the updated draft version. Please find the following responses for more details.

\subsection{Comments to section "CorShrink"}
After carefully reviewed \cite{dey2018}, we think it is very related to our paper and it is valuable to make the comparison.

@@

As mentioned in Section 1, our method is quite similar to \cite{dey2018}. Both of us used empirical Bayes estimator and nonparametric estimation of prior distribution. The difference is that our method aim to estimate covariance matrix which requires to also shrink standard deviations.

We also compared our two methods by numerical experiments which are shown in supporting information. We designed two simulations to compare the performance on correlation matrix estimation and covariance matrix estimation. In the first simulation, we compare covariance matrix estimation. For corShrink, $\widehat{\bs{\Sigma}} = \text{diag}(\widehat{SD}) \widehat{\bs{R}} \text{diag}(\widehat{SD})$, where $\widehat{SD}$ are sample standard deviations. In the second simulation, $\bs{\widehat{R}} = \text{diag}(1/\widehat{SD})\widehat{\bs{\Sigma}}\text{diag}(1/\widehat{SD})$, where $\widehat{SD}$ are standard deviations derived from $\widehat{\bs{\Sigma}}$. For each setting, we take $n$ as 20 and 100.

\subsection{Comments to section "Separable rules, symmetry and the diagonal"}
\begin{equation}\label{R1}
\widehat{\Sigma} = (\widehat{\sigma}_{jk})_{1\leq j,k\leq p},\quad \widehat{\sigma}_{jk} = t(X_{\cdot,j}, X_{\cdot,k}), \quad t:\bb{R}^n\times \bb{R}^n\to \bb{R}
\end{equation}
\begin{enumerate}
\item \emph{While reading the paper I was a bit confused by the fact that (R1) treats diagonal entries and off-diagonal in the same way. It would feel more natural to me to define a separable estimator as in (R1) for $j\neq k$, and as follows on the diagonal:}
$$\hat{\sigma}_{jj} = \tilde{t}(X_{\cdot j}),\quad \tilde{t}:\bb{R}^n \to \bb{R}$$
We have changed the rule to 
\begin{equation}
  \label{separable}
  \mathcal{S} = \{\bs{\delta} : \delta_{kj} = \delta_{jk} = t(\bs{X}_{\cdot j}, \bs{X}_{\cdot k}),\, 1\leq k<j\leq p,\quad 
   \delta_{jj} = \widetilde{t}(\bs{X}_{\cdot j}),\,j=1,\ldots,p)\},
\end{equation}
\emph{In the Multivariate Gaussian case this is not an issue, since $X_{\cdot j}\neq X_{\cdot k}$ for $j\neq k$ with probability 1. But the proposed approach would also apply with minor modifications to e.g., discrete measurements (with known likelihood) in which case $X_{\cdot j}\neq X_{\cdot k}$ could happen with non-zero probability.} \\
We agree that it is not very precise to use $I(\bs{X}_{\cdot j}=\bs{X}_{\cdot k})$ to differentiate on-diagonal entries and off-diagonal entries. So we changed separable rule to the above class of rules.

@@

In correspondence, we modified our sample exemplar algorithm, we first clusters sample points $(s_j,s_k, r_{jk})$ of lower triangular part of sample covariance matrix and get the $K$ centroids $(a,b,\gamma)$, then find their symmetric points $(b,a,\gamma)$. We also updated EM algorithm to guarantee each $(a,b,\gamma)$ and $(b,a,\gamma)$ has the same weight. 
\item \emph{The paper emphasizes the Multivariate Gaussian problem. In that case, the sample covariance is sufficient, and so, it would seem more natural to me to define a separable rule, as one that satisfies,
$$\hat{\sigma}_{jk} = \bar{t}(X_{\cdot j}^TX_{\cdot k}),\quad \bar{t}: \bb{R}\to \bb{R}_{+}$$
instead of (R1). I am wondering why the authors chose to use (R1) instead.}

$X_{\cdot j}^TX_{\cdot k}$ is sufficient statistics of the single entry $\sigma_{jk}$. In fact, for $(\bs{X}_{\cdot,j}, \bs{X}_{\cdot,k})$, the sufficient statistics for $\eta$ is $\bs{S}_{jk} = \begin{pmatrix} s_{jj}&s_{jk} \\  s_{kj}&s_{kk} \end{pmatrix}$. We also tried density based on single entries $s_{jk}$ before but the performance is not as good as using $(\bs{X}_{\cdot j},\bs{X}_{\cdot k})$.
\item \emph{If I understand correctly, one of the benefits of estimator (3) is that it works without specific assumptions on the noise distribution. Instead the approach here appears to more heavily rely on a known likelihood (and specifically a multivariate Gaussian likelihood). It would be great if some simulations could be conducted under misspecification, wherein the data is not multivariate Gaussian, but the approach is applied assuming multivariate Gaussian data.}

This is a good point. To measure the performance of our method on nonGaussian distribution, we did some simulations on negative binomial distribution. We first generate independent distributed $Y$ and then let $X = L Y$, where L is the Cholesky decomposition of $\Sigma$. The simulation results are presented in supporting information.
\end{enumerate}

\subsection{Comments to section "Compound decision theory or empirical Bayes?"}
\begin{enumerate}
\item \emph{The result following equation (6) could be presented separately as a Theorem (or Proposition). It should be highlighted that part of the statement is that the estimator in (R1) that optimizes (R2) depends on all the $\sigma_{j}$ and $\rho_{jk}$.}

@@

\end{thebibliography}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
